Robotic Cart System

### 2021-05-01 parts/10-introduction.tex
Update 10-introduction.tex

%----------------------------------------------------------------------
\section{Problem Statement}
%----------------------------------------------------------------------
Robotic carts are a prevalent invention designed to aid users in a number of important indoor and outdoor tasks. There are robotic systems currently available in the market that perform these tasks in a variety of ways. For example, in a grocery store, a customer may require the need of more than one cart but cannot push or pull two carts simultaneously. One major drawback, however, is that people with disabilities cannot push one cart let alone have a second cart to carry more items. Moreover, robots used for this purpose are costlier than they are worth.

@@

\vspace*{12pt}
\noindent
One such method that has been utilized to make a cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmissions technology~\cite{Sales2016-CompaRob}. Another method that has been implemented is the use of a GRU (Gated Recurrent Unit) network to detect shopping habits of customers while also using a LiDAR (Light Detection and Ranging) sensor and camera to detect and map the customer using a two-dimensional skeleton and follow the customer through the store~\cite{islam_lam_fukuda_kobayashi_kuno_2019}. Therein, authors utilized an Arduino MEGA 2560, six ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android Studio IDE device, and Bluetooth for detecting a customer and following them through the store~\cite{Rawashdeh2017-Person}.

@@

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
This report is organized into six chapters:

>>>>

%----------------------------------------------------------------------
\section{Motivation and Problem Statement}
%----------------------------------------------------------------------
Robotic carts are a prevalent invention designed to aid users in a number of important indoor and outdoor tasks. There are robotic systems currently available in the market that perform these tasks in a variety of ways. For example, in a grocery store, a customer may require the need of more than one cart but cannot push or pull two carts simultaneously. One major drawback, however, is that people with disabilities cannot push one cart let alone have a second cart to carry more items. Moreover, robots used for this purpose are more costly than they are worth.

@@

\vspace*{12pt}
\noindent
One such method, shown in Fig. \ref{fig:CompaRob}, that has been utilized to make a mobile cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmissions technology~\cite{Sales2016-CompaRob}. Another method, shown in Fig. \ref{fig:ShoppingSup}, that has been implemented is the use of a GRU (Gated Recurrent Unit) network to detect shopping habits of customers while also using a LiDAR (Light Detection and Ranging) sensor and camera to detect and map the customer using a two-dimensional skeleton and follow the customer through the store~\cite{islam_lam_fukuda_kobayashi_kuno_2019}. Therein, in Fig. \ref{fig:SmartCart}, authors utilized an Arduino MEGA 2560, six ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android Studio IDE device, and Bluetooth for detecting a customer and following them through the store~\cite{Rawashdeh2017-Person}.

\begin{figure}[b]
   \centering
   \includegraphics[width=0.4\textwidth]{figs/img/CompaRob}
   \caption{CompaRob Robot}
   \label{fig:CompaRob}
\end{figure}

\begin{figure}[b]
   \centering
   \includegraphics[width=0.38\textwidth]{figs/img/ShoppingSuportRobot}
   \caption{Shopping Support Robot}
   \label{fig:ShoppingSup}
\end{figure}

\begin{figure}[b]
   \centering
   \includegraphics[width=0.45\textwidth]{figs/img/SmartCart}
   \caption{Smart Cart Robot}
   \label{fig:SmartCart}
\end{figure}

@@

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
This report is organized into six chapters:
\todo[inline]{This section should go at the end of the chapter.}
